---
title: "Histograms"
author: "Johannes Vorster"
date: "17/10/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Import data

```{r}
library(readr)
library(dplyr)
library(ggplot2)
options(scipen=999)
data <- read_csv("D:\\Downloads\\TRG_DAT_CLN_RMV.csv")
head(data)
```

## Structure

```{r}
str(data)
```

## Data type changes

```{r}
data$PRODUCT_CODE <- factor(data$PRODUCT_CODE,ordered = TRUE,levels = c(paste("A",1:27,sep = "")))
data$PAYMENT_MODE <- as.factor(data$PAYMENT_MODE)
data$STATUS <- as.factor(data$STATUS)
data$ID_DOCUMENT_CODE <- as.factor(data$ID_DOCUMENT_CODE)
data$GENDER <- as.factor(data$GENDER)
data$MARITAL_STATUS <- as.factor(data$MARITAL_STATUS)
data$INSURED_ID_DESCRIPTION <- as.factor(data$INSURED_ID_DESCRIPTION)
data$INSURED_MARITAL_STATUS <- as.factor(data$INSURED_MARITAL_STATUS)
data$GENDER1 <- as.factor(data$GENDER1)
data$ID_DOCUMENT <- as.factor(data$ID_DOCUMENT)
```

## Histograms

## PRODUCT_CODE

```{r}
pdf(file = "PRODUCT_CODE.pdf")
ggplot(data, aes(x=PRODUCT_CODE)) + 
  geom_bar(color="black", fill="white") + 
  ylim(0,150000) + 
  labs(x = "Code", y = "Frequency")
```

## PREMIUM

```{r}
pdf(file = "PREMIUM.pdf")
ggplot(data, aes(x=PREMIUM)) + 
  geom_histogram(color="black", fill="white") + 
  ylim(0,300000) + 
  labs(x = "Rands", y = "Frequency")
pdf(file = "PREMIUM1005.pdf")
premium1005 <- data %>%
  select(PREMIUM) %>%
  filter(PREMIUM<=1005)
ggplot(premium1005, aes(x=PREMIUM)) + 
  geom_histogram(color="black", fill="white") + 
  labs(x = "Rands", y = "Frequency")
```

## INCOME

```{r}
pdf(file = "INCOME.pdf")
ggplot(data, aes(x=INCOME)) + 
  geom_histogram(color="black", fill="white") + 
  ylim(0,300000) + 
  labs(x = "Rands", y = "Frequency")
pdf(file = "INCOME30000.pdf")
income30000 <- data %>%
  select(INCOME) %>%
  filter(INCOME<=30000)
ggplot(income30000, aes(x=INCOME)) + 
  geom_histogram(color="black", fill="white") + 
  ylim(0,60000) + 
  labs(x = "Rands", y = "Frequency")
```

## PAYMENT_MODE

```{r}
pdf(file = "PAYMENT_MODE.pdf")
ggplot(data, aes(x=PAYMENT_MODE)) + 
  geom_bar(color="black", fill="white") + 
  ylim(0,125000) + 
  labs(x = "Mode", y = "Frequency")
```

## STATUS

```{r}
pdf(file = "STATUS.pdf")
ggplot(data, aes(x=STATUS)) + 
  geom_bar(color="black", fill="white") + 
  ylim(0,200000) + 
  labs(x = "Status", y = "Frequency")
pdf(file = "ACT.pdf")
data$STATUS <- as.character(data$STATUS)
active <- data %>%
  select(STATUS) %>%
  mutate(STATUS = replace(STATUS, STATUS!="ACT", "NOT_ACT"))
active$STATUS <- as.factor(active$STATUS)
ggplot(active, aes(x=STATUS)) + 
  geom_bar(color="black", fill="white") + 
  ylim(0,200000) + 
  labs(x = "Status", y = "Frequency")
```

## STATUS_DATE

```{r}
pdf(file = "STATUS_DATE.pdf")
ggplot(data, aes(x=STATUS_DATE)) + 
  geom_histogram(color="black", fill="white") + 
  ylim(0,20000) + 
  labs(x = "Date", y = "Frequency")
```

## COMMENCEMENT_DATE

```{r}
pdf(file = "COMMENCEMENT_DATE.pdf")
ggplot(data, aes(x=COMMENCEMENT_DATE)) + 
  geom_histogram(color="black", fill="white") + 
  ylim(0,25000) + 
  labs(x = "Date", y = "Frequency")
```

## TERM

```{r}
pdf(file = "TERM.pdf")
ggplot(data, aes(x=TERM)) + 
  geom_histogram(color="black", fill="white") + 
  ylim(0,150000) + 
  labs(x = "Term", y = "Frequency")
```

## ID_DOCUMENT_CODE

```{r}
pdf(file = "ID_DOCUMENT_CODE.pdf")
ggplot(data, aes(x=ID_DOCUMENT_CODE)) + 
  geom_bar(color="black", fill="white") + 
  ylim(0,300000) + 
  labs(x = "Code", y = "Frequency")
```

## OCCUPATION_CODE

```{r}
pdf(file = "OCCUPATION_CODE.pdf")
ggplot(data, aes(x=OCCUPATION_CODE)) + 
  geom_histogram(color="black", fill="white") + 
  ylim(0,50000) + 
  labs(x = "Code", y = "Frequency")
```

## PAYER_DATE_OF_BIRTH

```{r}
pdf(file = "PAYER_DATE_OF_BIRTH.pdf")
ggplot(data, aes(x=PAYER_DATE_OF_BIRTH)) + 
  geom_histogram(color="black", fill="white") + 
  ylim(0,40000) + 
  labs(x = "Date", y = "Frequency")
```

## GENDER

```{r}
pdf(file = "GENDER.pdf")
ggplot(data, aes(x=GENDER)) + 
  geom_bar(color="black", fill="white") + 
  ylim(0,150000) + 
  labs(x = "Gender", y = "Frequency")
```

## MARITAL_STATUS

```{r}
pdf(file = "MARITAL_STATUS.pdf")
ggplot(data, aes(x=MARITAL_STATUS)) + 
  geom_bar(color="black", fill="white") + 
  ylim(0,200000) + 
  labs(x = "Marital status", y = "Frequency")
pdf(file = "GENDER_MARITAL_STATUS.pdf")
ggplot(data) +
  geom_bar(aes(x=MARITAL_STATUS, fill=GENDER),position=position_dodge()) + 
  ylim(0,125000) + 
  labs(x = "Status", y = "Frequency")
```

## INSURED_ID_DESCRIPTION

```{r}
pdf(file = "INSURED_ID_DESCRIPTION.pdf")
ggplot(data, aes(x=INSURED_ID_DESCRIPTION)) + 
  geom_bar(color="black", fill="white") + 
  ylim(0,300000) + 
  labs(x = "Code", y = "Frequency")
```

## INSURED_DATE_OF_BIRTH

```{r}
pdf(file = "INSURED_DATE_OF_BIRTH.pdf")
ggplot(data, aes(x=INSURED_DATE_OF_BIRTH)) + 
  geom_histogram(color="black", fill="white") + 
  ylim(0,40000) + 
  labs(x = "Date", y = "Frequency")
```

## INSURED_GENDER

```{r}
pdf(file = "INSURED_GENDER.pdf")
ggplot(data, aes(x=INSURED_GENDER)) + 
  geom_bar(color="black", fill="white") + 
  ylim(0,155000) + 
  labs(x = "Gender", y = "Frequency")
```

## INSURED_MARITAL_STATUS

```{r}
pdf(file = "INSURED_MARITAL_STATUS.pdf")
ggplot(data, aes(x=INSURED_MARITAL_STATUS)) + 
  geom_bar(color="black", fill="white") + 
  ylim(0,205000) + 
  labs(x = "Status", y = "Frequency")
pdf(file = "INSURED_GENDER_MARITAL_STATUS.pdf")
ggplot(data) +
  geom_bar(aes(x=INSURED_MARITAL_STATUS, fill=INSURED_GENDER),position=position_dodge()) + 
  ylim(0,125000) + 
  labs(x = "Status", y = "Frequency")
```

## PAYPOINT_NAME

```{r}
pdf(file = "PAYPOINT_NAME.pdf")
ggplot(data, aes(x=PAYPOINT_NAME)) + 
  geom_histogram(color="black", fill="white") + 
  ylim(0,125000) + 
  labs(x = "Code", y = "Frequency")
```

## DATE_OF_BIRTH

```{r}
pdf(file = "DATE_OF_BIRTH.pdf")
ggplot(data, aes(x=DATE_OF_BIRTH)) + 
  geom_histogram(color="black", fill="white") + 
  ylim(0,50000) + 
  labs(x = "Date", y = "Frequency")
```

## GENDER1

```{r}
pdf(file = "GENDER1.pdf")
ggplot(data, aes(x=GENDER1)) + 
  geom_bar(color="black", fill="white") + 
  ylim(0,150000) + 
  labs(x = "Gender", y = "Frequency")
```

## ID_DOCUMENT

```{r}
pdf(file = "ID_DOCUMENT.pdf")
ggplot(data, aes(x=ID_DOCUMENT)) + 
  geom_bar(color="black", fill="white") + 
  ylim(0,250000) + 
  labs(x = "Code", y = "Frequency")
```

## ps_lapse1

```{r}
pdf(file = "ps_lapse1.pdf")
ggplot(data, aes(x=ps_lapse1)) + 
  geom_histogram(color="black", fill="white") + 
  ylim(0,200000) + 
  labs(x = "Percentage", y = "Frequency")
```

## nbank

```{r}
pdf(file = "nbank.pdf")
ggplot(data, aes(x=nbank)) + 
  geom_bar(color="black", fill="white") + 
  ylim(0,80000) + 
  labs(x = "Number of banks", y = "Frequency")
```

## nloans

```{r}
pdf(file = "nloans.pdf")
ggplot(data, aes(x=nloans)) + 
  geom_bar(color="black", fill="white") + 
  scale_x_discrete(limits=factor(1:9)) + 
  ylim(0,40000) + 
  labs(x = "Number of loans", y = "Frequency")
```

