---
title: "Data cleaning"
author: "Johannes Vorster"
date: "12/10/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Import data

```{r}
library(readxl)
library(dplyr)
data <- read_excel("D:/Downloads/TRG_DAT.xlsx")
head(data)
```

## Structure

```{r}
str(data)
```

## Data type changes

```{r}
data$PRODUCT_CODE <- as.factor(data$PRODUCT_CODE)
data$INCOME <- as.numeric(data$INCOME)
data$PAYMENT_MODE <- as.factor(data$PAYMENT_MODE)
data$STATUS <- as.factor(data$STATUS)
data$STATUS_DATE <- as.Date(data$STATUS_DATE)
data$COMMENCEMENT_DATE <- as.Date(data$COMMENCEMENT_DATE)
data$ID_DOCUMENT_CODE <- as.factor(data$ID_DOCUMENT_CODE)
data$PAYER_DATE_OF_BIRTH <- as.Date(data$PAYER_DATE_OF_BIRTH)
data$GENDER <- as.factor(data$GENDER)
data$MARITAL_STATUS <- as.factor(data$MARITAL_STATUS)
data$TITLE <- as.factor(data$TITLE)
data$INSURED_ID_DESCRIPTION <- as.factor(data$INSURED_ID_DESCRIPTION)
data$INSURED_DATE_OF_BIRTH <- as.Date(data$INSURED_DATE_OF_BIRTH)
data$INSURED_GENDER <- as.factor(data$INSURED_GENDER)
data$INSURED_MARITAL_STATUS <- as.factor(data$INSURED_MARITAL_STATUS)
data$INSURED_TITLE <- as.factor(data$INSURED_TITLE)
data$DATE_OF_BIRTH <- as.Date(data$DATE_OF_BIRTH)
data$GENDER1 <- as.factor(data$GENDER1)
data$ID_DOCUMENT <- as.factor(data$ID_DOCUMENT)
```

## Corrections

## POLICY_NUMBER

```{r}
data %>%
  group_by(POLICY_NUMBER) %>%
  filter(n()>1) %>%
  count(POLICY_NUMBER)
#data <- subset(data,select = -c(POLICY_NUMBER))
```

## PRODUCT_CODE

```{r}
summary(data$PRODUCT_CODE)
```

## PREMIUM

```{r}
summary(data$PREMIUM)
data %>%
  tally(PREMIUM<0)
quantile(data$PREMIUM,seq(0,1,0.1))
# data %>%
#   filter(PREMIUM>1005)
data <- data %>%
  filter(!(PREMIUM<0))
```

## INCOME

```{r}
summary(data$INCOME)
data %>%
  tally(INCOME==0)
# quantile(data$INCOME,seq(0,1,0.1),na.rm = TRUE)
# data %>%
#   filter(INCOME>30000)
# data <- data %>%
#   filter(!(INCOME>30000))
```

## PAYMENT_METHOD

```{r}
summary(data$PAYMENT_MODE)
data <- data %>%
  mutate(PAYMENT_MODE = replace(PAYMENT_MODE, PAYMENT_MODE=="Add", "ADD"))
data$PAYMENT_MODE <- droplevels(data$PAYMENT_MODE,factor("Add"))
data <- data %>%
  filter(!(PAYMENT_MODE=="PLS"))
data$PAYMENT_MODE <- droplevels(data$PAYMENT_MODE,factor("PLS"))
summary(data$PAYMENT_MODE)
```

## STATUS

```{r}
summary(data$STATUS)
data <- data %>%
  mutate(STATUS = replace(STATUS, STATUS=="Act", "ACT")) %>%
  mutate(STATUS = replace(STATUS, STATUS=="Lap", "LAP"))
data$STATUS <- droplevels(data$STATUS,factor(c("Act","Lap")))
data <- data %>%
  filter(!(STATUS=="TRM"))
data$STATUS <- droplevels(data$STATUS,factor("TRM"))
summary(data$STATUS)
```

## STATUS_DATE

```{r}
summary(data$STATUS_DATE)
data %>%
  tally(STATUS_DATE<COMMENCEMENT_DATE)
```

## COMMENCEMENT_DATE

```{r}
summary(data$COMMENCEMENT_DATE)
data %>%
  tally(COMMENCEMENT_DATE<PAYER_DATE_OF_BIRTH)
data %>%
  tally(COMMENCEMENT_DATE<INSURED_DATE_OF_BIRTH)
data %>%
  tally(COMMENCEMENT_DATE<DATE_OF_BIRTH)
```

## TERM

```{r}
summary(data$TERM)
data %>%
  filter(TERM>99) %>%
  count(TERM)
data <- data %>%
  filter(!(TERM>99))
summary(data$TERM)
```

## PAYFREQ

```{r}
summary(data$PAYFREQ)
data %>%
  count(PAYFREQ)
data <- data %>%
  filter(!(PAYFREQ==147))
summary(data$PAYFREQ)
#data <- subset(data,select = -c(PAYFREQ))
```

## ID_DOCUMENT_CODE

```{r}
summary(data$ID_DOCUMENT_CODE)
data <- data %>%
  filter(!(ID_DOCUMENT_CODE==3 | ID_DOCUMENT_CODE==4))
data$ID_DOCUMENT_CODE <- droplevels(data$ID_DOCUMENT_CODE,factor(c(3,4)))
summary(data$ID_DOCUMENT_CODE)
```

## OCCUPATION_CODE

```{r}
data %>%
  count(OCCUPATION_CODE) %>%
  arrange(desc(n))
```

## PAYER_DATE_OF_BIRTH

```{r}
summary(data$PAYER_DATE_OF_BIRTH)
data %>%
  tally(PAYER_DATE_OF_BIRTH>"2018-08-01")
not_happend_yet <- as.numeric(data$PAYER_DATE_OF_BIRTH>"2018-08-01")
data$PAYER_DATE_OF_BIRTH <- data$PAYER_DATE_OF_BIRTH-36525*not_happend_yet
data %>%
  tally(COMMENCEMENT_DATE<PAYER_DATE_OF_BIRTH)
data <- data %>%
  filter(!(COMMENCEMENT_DATE<PAYER_DATE_OF_BIRTH))
```

## GENDER

```{r}
summary(data$GENDER)
data <- data %>%
  filter(!(GENDER=="MFMFMF"))
data$GENDER <- droplevels(data$GENDER,factor("MFMFMF"))
summary(data$GENDER)
```

## MARITAL_STATUS

```{r}
summary(data$MARITAL_STATUS)
```

## TITLE

```{r}
summary(data$TITLE)
data <- data %>%
  mutate(TITLE = replace(TITLE, TITLE=="MR.", "MR"))
data$TITLE <- droplevels(data$TITLE,factor("MR."))
summary(data$TITLE)
#data <- subset(data,select = -c(TITLE))
```

## INSURED_ID_DESCRIPTION

```{r}
summary(data$INSURED_ID_DESCRIPTION)
```

## OCCUPATION_DESC1

```{r}
data %>%
  count(OCCUPATION_DESC1)
#data <- subset(data,select = -c(OCCUPATION_DESC1))
```

## INSURED_DATE_OF_BIRTH

```{r}
summary(data$INSURED_DATE_OF_BIRTH)
data %>%
  tally(INSURED_DATE_OF_BIRTH>"2018-08-01")
not_happend_yet <- as.numeric(data$INSURED_DATE_OF_BIRTH>"2018-08-01")
data$INSURED_DATE_OF_BIRTH <- data$INSURED_DATE_OF_BIRTH-36525*not_happend_yet
data %>%
  tally(COMMENCEMENT_DATE<INSURED_DATE_OF_BIRTH)
data <- data %>%
  filter(!(COMMENCEMENT_DATE<INSURED_DATE_OF_BIRTH))
```

## INSURED_GENDER

```{r}
summary(data$INSURED_GENDER)
```

## INSURED_MARITAL_STATUS

```{r}
summary(data$INSURED_MARITAL_STATUS)
```

## INSURED_TITLE

```{r}
summary(data$INSURED_TITLE)
data <- data %>%
  mutate(INSURED_TITLE = replace(INSURED_TITLE, INSURED_TITLE=="MR.", "MR"))
data$INSURED_TITLE <- droplevels(data$INSURED_TITLE,factor("MR."))
summary(data$INSURED_TITLE)
#data <- subset(data,select = -c(INSURED_TITLE))
```

## PAYPOINT_NAME

```{r}
data %>%
  count(PAYPOINT_NAME)
data$PAYPOINT_NAME <- gsub("Paypoint","",data$PAYPOINT_NAME)
data$PAYPOINT_NAME <- as.numeric(data$PAYPOINT_NAME)
summary(data$PAYPOINT_NAME)
```

## COMPANY_NAME

```{r}
data %>%
  count(COMPANY_NAME)
data$COMPANY_NAME <- gsub("Comp","",data$COMPANY_NAME)
data$COMPANY_NAME <- as.numeric(data$COMPANY_NAME)
summary(data$COMPANY_NAME)
#data <- subset(data,select = -c(COMPANY_NAME))
```

## DATE_OF_BIRTH

```{r}
summary(data$DATE_OF_BIRTH)
data %>%
  tally(DATE_OF_BIRTH>"2018-08-01")
not_happend_yet <- as.numeric(data$DATE_OF_BIRTH>"2018-08-01")
data$DATE_OF_BIRTH <- data$DATE_OF_BIRTH-36525*not_happend_yet
data %>%
  tally(COMMENCEMENT_DATE<DATE_OF_BIRTH)
data <- data %>%
  filter(!(COMMENCEMENT_DATE<DATE_OF_BIRTH))
```

## GENDER1

```{r}
summary(data$GENDER1)
```

## ID_DOCUMENT

```{r}
summary(data$ID_DOCUMENT)
data <- data %>%
  filter(!(ID_DOCUMENT==12))
data$ID_DOCUMENT <- droplevels(data$ID_DOCUMENT,factor(12))
summary(data$ID_DOCUMENT)
```

## ps_lapse1

```{r}
summary(data$ps_lapse1)
data %>%
  tally(ps_lapse1<0)
data <- data %>%
  filter(!(ps_lapse1<0))
```

## xx

```{r}
#data <- subset(data,select = -c(xx))
```

## ee

```{r}
#data <- subset(data,select = -c(ee))
```

## nbank

```{r}
data %>%
  count(nbank)
```

## nloans

```{r}
data %>%
  count(nloans)
```

## NAS

```{r}
sapply(data, function(x) sum(is.na(x)))
```

## Summary

```{r}
summary(data)
```

## Export

```{r}
write.csv(data,"D:\\Downloads\\TRG_DAT_CLN_KEEP.csv", row.names = FALSE)
```

